The \dealii Library, Version 9.4

### 2022-06-24 9.4/paper.tex
release date

\dealii version 9.4.0 was released June 10, 2022.
\todo{Update release date.}
This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii software library version 9.4. \dealii is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL). Downloads are available at
\url{https://www.dealii.org/} and \url{https://github.com/dealii/dealii}.

>>>>

\dealii version 9.4.0 was released June 24, 2022.
This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii software library version 9.4. \dealii is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL). Downloads are available at
\url{https://www.dealii.org/} and \url{https://github.com/dealii/dealii}.
